Constant-round Blind Classical Verification of Quantum Sampling

### 2020-08-23 qpip0.tex
Fix another typo

	By property~\ref{property:partition-binding} of Lemma~\ref{lem:partition2}, the above strategy is accepted with probability $1-\negl(n)$ when the prover didn't abort.
	Since the prover's strategy is also efficient, by Lemma~\ref{lem:naive-qpip0-binding},
	$z_{composite,}$ is $O(\eps)$-computationally indistinguishable to $z_{ideal, i}$.
\end{proof}

>>>>

	By property~\ref{property:partition-binding} of Lemma~\ref{lem:partition2}, the above strategy is accepted with probability $1-\negl(n)$ when the prover didn't abort.
	Since the prover's strategy is also efficient, by Lemma~\ref{lem:naive-qpip0-binding},
	$z_{composite}$ is $O(\eps)$-computationally indistinguishable to $z_{ideal, i}$.
\end{proof}
